---
title: "Stormglass Weather"
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
library(flextable)
  set_flextable_defaults(font.family = 'sans', theme_fun = "theme_zebra", 
        font.size = 11, text.align = "right",padding.left = 1, padding.right = 1,
        padding.top = 2, padding.bottom = 2, na_str="–")
```

The weather request is used to fetch weather data for a point. The Storm Glass
API provides marine weather as well as global weather for land and lakes.

To get marine data you include a coordinate at sea in your request, and to get
data for land and lakes - simply send in a coordinate located on land or on a
lake.

### Point Request

Point Requests are used to retrieve data for a single coordinate.

GET <https://api.stormglass.io/v2/weather/point>

### Available Query Parameters

```{r query-params, echo=FALSE}
qp <- read.csv("stormglass-qp.csv")
flextable(qp) |> width(width=c(2,2,3.5,10.5), unit="cm") |>
  align(j=2, align="center") |> font(j=1, fontname = "Courier New") |> 
  fontsize(j=1, size=10) |> valign(valign="top")
```

### Response Format

The response will be sent back in the form of a JSON object. The resource root
contains two objects - data and meta.

*Meta*

The meta object contains information about the API request. Such as requested
latitude and longitude, your daily quota and how many requests you have made so
far today.

*Data*

The data object contains the actual weather data on an hourly basis. One item in
the data array can contain:

```{r output-params, echo=F}
op <- read.csv("stormglass-output-parameters.csv")
flextable(op) |> width(width=c(4,13), unit="cm") |>
  font(j=1, fontname = "Courier New") |> 
  fontsize(j=1, size=10) |> valign(valign="top")
```
&nbsp;  

Each parameter (*e.g*. `swellHeight`) is an object that contains a key and value
for each available source, *i.e*. { sg: 10.3 }.

### Example using `R` code

```{r example-r-code, eval=FALSE}
library(httr)
library(jsonlite)
library(lubridate)

# set start time
start <- as.POSIXct("2022-06-01 00:00:00")

# set end date
end <- as.POSIXct("2022-06-30 23:59:59")

# API endpoint and parameters
url <- "https://api.stormglass.io/v2/weather/point"
params <- list(
  lat = 35.288,
  lng = 113.894,
  params = paste(c("precipitation","airTemperature","windDirection","windSpeed"),
                 collapse = ","),
  start = as.numeric(start),
  end = as.numeric(end)
)

# API headers
headers <- c("Authorization" = secret) # secret contains API key!

# Make the API request
response <- GET(url, query = params, add_headers(.headers=headers))

# Convert response to JSON
json_data <- fromJSON(content(response, "text"))

# Do something with response data.
# (Note: You may need to adjust the data processing steps based on the structure of the JSON response)
print(json_data)
```
